How fluid-mechanical erosion creates anisotropic porous media

### 2022-12-15 docs/PhysicsPaper/StokesErosion.tex
NM

Our method merges \edit{spectrally}-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies embedded in \edit{two-dimensional Stokes flows.}
Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulation of dense suspensions of erodable bodies~\cite{chiu2020viscous}. Though the governing Stokes equations are linear, the nonlinear feedback between evolving microstructure and flow gives rise to highly complex and anisotropic configurations.

@@

The embedded bodies may erode in response to the shear stresses induced by the intervening fluid flow. Erosion typically occurs over much longer timescales than the fluid flow, permitting a {\em quasi-steady} approximation. In this approximation, the configuration of bodies is held fixed in order to compute the {\em steady} Stokes flow determined by~\eqref{eqn:StokesEq}, and then this flow field determines the stresses acting to erode each body. We employ an erosion law in which the local rate of material loss is linearly proportional to the magnitude of the shear stress $\tau$ acting on the surface~\cite{Ristroph2012, Moore2013, Mitchell2016, MooreCPAM2017, HewettJFS2017, quaife2018boundary, chiu2020viscous}. The material loss gives rise to an inward velocity of the solid surface, $\Vn$, pointing in the direction normal to the surface. The erosion law is thus expressed as
\begin{align}
\Vn &= \CE \, \abs{\tau}, 
	\hspace{88pt} \xx \in \gamma, &&\mbox{\em erosion model}, 
\label{Vn0} \\
\tau &= - \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss,
	\hspace{20pt} \xx \in \gamma, &&\mbox{\em shear stress}.
\label{tau0}
\end{align}
where $\nn$ is the unit normal vector pointing into each body, $\ss$ is the unit tangent vector pointing in the counterclockwise direction, and $\CE$ is a material-dependent erosion constant.
\edit{For numerical stability, we will modify this law in Section \ref{sec:int_evo} to include a smoothing term that depends on the local curvature of each body.}

>>>>

Our method merges \edit{spectrally}-accurate boundary-integral equation (BIE) methods~\cite{baker1986boundary, moore2007evaluation, gray2019boundary} with stable interface evolution methods~\cite{hou-low-she1994, Moore2013} to simulate the erosion of dense suspensions of solid bodies embedded in \edit{two-dimensional Stokes flows.}
Originally inspired by related work in the high-Reynolds-number regime~\cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017}, our method is documented, validated, benchmarked in~\cite{quaife2018boundary}, and can simulate the erosion of $O(100)$ solid bodies. The more recent Cauchy reformulation of the BIE and the associated quadrature formulas allow us to resolve points of near contact between bodies, thus enabling high-fidelity simulations of dense suspensions of erodable bodies~\cite{chiu2020viscous}. Though the governing Stokes equations are linear, the nonlinear feedback between evolving microstructure and flow gives rise to highly complex and anisotropic configurations.

@@

The embedded bodies may erode in response to the shear stresses induced by the intervening fluid flow. Erosion typically occurs over much longer timescales than the fluid flow, permitting a {\em quasi-steady} approximation. In this approximation, the configuration of bodies is held fixed in order to compute the {\em steady} Stokes flow determined by~\eqref{eqn:StokesEq}, and then this flow field determines the stresses acting to erode each body. We employ an erosion law in which the local rate of material loss is linearly proportional to the magnitude of the shear stress $\tau$ acting on the surface~\cite{Ristroph2012, Moore2013, Mitchell2016, MooreCPAM2017, HewettJFS2017, quaife2018boundary, chiu2020viscous}. The material loss gives rise to an inward velocity of the solid surface, $\Vn$, pointing in the direction normal to the surface. The erosion law is thus expressed as
\begin{align}
\Vn &= \CE \, \abs{\tau}, 
	\hspace{82pt} \xx \in \gamma, &&\mbox{\em erosion model}, 
\label{Vn0} \\
\tau &= - \left( ( \nabla \uu + \nabla \uu^T) \nn \right) \cdot \ss,
	\hspace{20pt} \xx \in \gamma, &&\mbox{\em shear stress}.
\label{tau0}
\end{align}
where $\nn$ is the unit normal vector pointing into each body, $\ss$ is the unit tangent vector pointing in the counterclockwise direction, and $\CE$ is a material-dependent erosion constant.
\edit{For numerical stability, we will modify this law in Section \ref{sec:int_evo} to include a smoothing term that depends on the local curvature of each body.}
